%\section{Feature extraction} 
	
Before training the classifier, features were extracted from the signal. The raw EMG-signal from each MYB-channel was segmented into 200 ms windows with a 50\% overlap respecting the findings of Farfán et al. \cite{Farfan2010}. Based on using the MYB for data acquisition recommendations made by Donovan et al. \cite{Donovan2017} regarding the optimal features for low bandwidth sEMG pattern recognition were taken into consideration. These features proved to provide useful signal information even though the MYB only samples sEMG signals with 200 Hz, and in this case offering better accuracy than the Hudgins features \cite{Hudgins1993} in a LDA based control scheme \cite{Donovan2017}. \\
Four space domain (SD) features of Scaled Mean Absolute Value (SMAV), Correlation Coefficient (CC), Mean Absolute Difference Normalized (MADN), Scaled Mean Absolute Difference Raw (SMADR) were used for feature extraction. These features represent some of the features Donavan et al. \cite{Donovan2017} proposed as the rest were left unused due to the intent of reducing feature redundancy. The calculation of SD features lean on the calculation and relation of other SD features. Special for the SD features is utilizing the relation between signals acquired in the different channels of the MYB. Additionally the well known Hudgins time domain feature Waveform Length (WL) was included to cover complexity information in the time domain \cite{Phiny2012}. %These features were chosen with the aim of acquiring valuable signal information from both signal amplitude and frequency.  
