\section{Study protocol}

\textbf{Title of project}

Using estimation uncertainty to improve prosthesis control 

\textbf{Detail on investigators}

All investigators are currently 8th. semester students, studying at Aalborg University.  

\textbf{Purpose and background}

Commercially available prosthesis have yet to adopt the use of pattern recognition methods in their control scheme. Mainly, this is due to the disadvantages exploited in “ref til introduction om problemer måske?”. A control scheme that reduce these disadvantages are therefore sought through the combination of regression and classification based methods. 
The overall aim is to develop a novel control scheme for myoelectric prosthetic devices. Hereby it is sought to clarify if a combined regression and classification control scheme yields higher subject performance in a Fitts’ Law test compared to a method only using regression.         

\textbf{Research question/hypothesis}

The use of a Fitts’s Law test will show a significant improvement in subject prosthesis control with a combined regression and classification control scheme compared to a method using only regression. 

\textbf{Ethical considerations}  

The investigators do not foresee any obstacles of ethical nature during the proceedings of this experiment. No test subjects will be exposed to any physical interventions besides being asked to wear the Myo armband. No part of this experiment should put the subject in danger. 

\textbf{Session time} 

The experiment consist of one session divided into two sub-sessions with an estimated total duration of 2-3 hours.

\textbf{Inclusion criteria}

The subject needs to be:
\begin{itemize}
	\item able bodied.
	\item between 18 and 35 years of age.
	\item able to understand and speak Danish and/or English.
	\item assessed by the investigators to understand and perform the instructions given during the experiment. 
\end{itemize}


\textbf{Exclusion criteria}

The subject must not have:
\begin{itemize}
	\item diseases that might influence subject performance   
\end{itemize}


\textbf{Experiment procedure}

The experiment is divided into two sessions: 1) training data acquisition, user training and performance test and 2) new training data acquisition and performance test. During the training data acquisition EMG data will be recorded from the subject with an EMG-electrode armband(Myoband from Thalmic Labs) when performing four different wrist movements(flexion, extension, radial deviation and ulnar deviation) as illustrated in \figref{FIGURE}. The data is subsequently used to fit a classification model used in the myoelectric control scheme for the following user training and performance test. Before the performance test the user is given a training period to get familiar with wrist movements used in the performance test. During the performance test the subject will perform a target-reaching task in a cartesian coordinate system of reaching a number of targets using wrist movements, where each axis represent a one of four wrist movements, as seen in figure \figref{FIGURE2}. The aim for the subject is to reach as many targets as quickly as possible. The subject will perform the target-reaching task twice - one in each session. The subject are divided into two groups: a test group and a control group. As the study is single-blinded the subject will not be informed which group he/she belongs to.

Chronology of session 1):
\begin{enumerate}
	\item Apply Myoband on dominant forearm at the thickest part.
	\item Synchronize Myoband by performing wrist extension until three distinct vibrations are felt.
	\item Perform 15 seconds of maximum voluntary contraction(MVC) of instructed movement. Following the MVC the subject will be given a 30 resting period to avoid fatigue.
	\item Perform 15 seconds contractions of respectively 20\%, 40\% and 60\% of MVC. During these contractions the subject will control a green marker representing the EMG signal and try to follow a trapezoidal trajectory a precise as possible. The trapezoidal trajectory consists of two five second transition phases and one five second plateau phase as illustrated in figure \figref{FIGURE3}. Between each trial the subject will be given a 15 seconds resting period to avoid muscle fatigue.
	\item Repeat step 3-4 until training data from all four wrist movements has been recorded.
	\item The subject will train the four wrist movements. Each movement will be performed 10 times, where each single movement consists of a five second movement with increased intensity. To improve the precision of movements the subject will receive visual feedback consisting of the probability the movement to belong to based on the classifier. The ideal probability during the training is a 100\% probability of belonging to the trained movement and a 0\% probability of belonging to the remaining movements. 
	\item The subject will perform a target-reaching task. The subject will control an arrow originated from origo in a cartesian coordinate system representing the features extracted from the EMG data, where the length represent the intensity and direction depicts the movement performed. To reach a target the subject must dwell the head of the arrow within the target for 0.5 seconds. If this is achieved the target will disappear. The target will similarly disappear if the subject fails to achieve this within 15 seconds. When an outer target disappears a target centred in origo appears and the subject must reach this before a new outer target appears. This procedure is continued until no more targets are shown. After finishing the performance test the subject will be given a 2 minutes resting period.


Chronology of session 2):
\begin{enumerate}
	 \item Perform step 3-5 from session 1.
	 \item Perform step 7 from session 1. 
\end{enumerate}
 







